Reproducible Data Peer Assignment 1
=======================================================

This is my first R markdown file.

Load the activity.csv file into R.

```{r}
activity <- read.csv("./Data/activity.csv")
summary (activity)
str(activity)
```

Remove the NA values using the complete function and store it into the a new data frame.

```{r}
activityComplete <- activity[complete.cases(activity),]
summary (activityComplete)
str(activityComplete)
```

Create a dataframe with aggregated steps taken each day.

``` {r}
stepsByDate <-aggregate(activityComplete$steps, by=list(Category=activityComplete$date),FUN=sum)
names(stepsByDate) <- c("date", "steps")
summary(stepsByDate)
str(stepsByDate)
```

Create histogram of steps taken each day.
```{r}
hist(stepsByDate$steps)
```

Calculate mean and media total number of steps taken per day.
```{r}
mean(stepsByDate$steps)
median(stepsByDate$steps)
```

Create data frame of average steps taken at a time interval accross all days.
```{r}
AvgstepsByInterval <-aggregate(activityComplete$steps, by=list(Category=activityComplete$interval),FUN=mean)
names(AvgstepsByInterval) <- c("interval", "steps")
summary(AvgstepsByInterval)
str(AvgstepsByInterval)
```

Create line plot
```{r}
plot(AvgstepsByInterval$interval,AvgstepsByInterval$steps, type="l")
```

Calculate number of rows coded as NA
```{r}
sum(is.na(activity$steps))
```

Merge the average steps by interval with the activity table
```{r}
mergeActivity <- merge(activity, AvgstepsByInterval, by.x = "interval", by.y="interval", all=TRUE)
```
Replace all NA values in steps with the average steps for that interval
```{r}
mergeActivity <- transform(mergeActivity, steps.x = ifelse(is.na(steps.x),steps.y,steps.x))
mergeActivity <- data.frame(mergeActivity[,c(1,2,3)])
names(mergeActivity) <- c("interval", "steps", "date")
summary(mergeActivity)
str(mergeActivity)
```
Create a dataframe with aggregated steps taken each day for the new dataset
``` {r}
stepsByDate <-aggregate(mergeActivity$steps, by=list(Category=mergeActivity$date),FUN=sum)
names(stepsByDate) <- c("date", "steps")
summary(stepsByDate)
str(stepsByDate)
```
Create histogram of steps taken each day for the new dataset
```{r}
hist(stepsByDate$steps)
```
Calculate mean and media total number of steps taken per day for the new dataset
```{r}
mean(stepsByDate$steps)
median(stepsByDate$steps)
```
Append Day of week to the dataframe with the NA replaced
```{r}
mergeActivity$DayOfWeek <-weekdays(as.POSIXlt(mergeActivity$date, format="%Y-%m-%d"))
```
Create Day of Week to Type of Day Crosswalk
```{r}
dayOfWeekTbl <- data.frame(cbind(c("Monday", "Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday"), c("Weekday", "Weekday", "Weekday", "Weekday", "Weekday","Weekend", "Weekend")))
names(dayOfWeekTbl) <- c("DayOfWeek", "DayType")
dayOfWeekTbl
```
Merge Day of Week table with mergeActivity table. 
```{r}
mergeActivity <-merge(mergeActivity, dayOfWeekTbl, by.x = "DayOfWeek", by.y="DayOfWeek", all=TRUE)
summary(mergeActivity)
str(mergeActivity)
```
Create data frame of average steps taken at a time interval accross all days with day type.
```{r}
MergedAvgstepsByInterval <-aggregate(mergeActivity$steps, by=list(interval=mergeActivity$interval, DayType=mergeActivity$DayType),FUN=mean)
names(MergedAvgstepsByInterval) <- c("interval", "DayType", "steps")
summary(MergedAvgstepsByInterval)
str(MergedAvgstepsByInterval)
```
Create lattice plot Plot
```{r}
library(lattice)
xyplot(steps~interval|DayType, data=MergedAvgstepsByInterval, layout=c(1,2), type="l")
```

